\Huge\textbf{Mbrane}\linebreak\linebreak\linebreak \Large\textbf{Final Report}\linebreak\linebreak \linebreak\linebreak \includegraphics[scale=0.1]{feup-logo.png}\linebreak\linebreak \linebreak\linebreak \Large{Logic Programing}\linebreak

### 2019-11-17 docs/report_latex/template.tex

Descrever o projeto e implementação da lógica do jogo em Prolog, incluindo a forma de representação do estado do tabuleiro e sua visualização, execução de movimentos, verificação do cumprimento das regras do jogo, determinação do final do jogo e cálculo das jogadas a realizar pelo computador utilizando diversos níveis de jogo. Sugere-se a estruturação desta secção da seguinte forma:

@@

% TODO complete
\subsection{Board viewing} 
Descrever a interface com o utilizador, descrevendo a visualização do estado do jogo (pode ser idêntico ao descrito no relatório intercalar) e robustez da interface/validações de entrada.

% TODO complete
\subsection{List valid plays} 
Obtenção de uma lista de jogadas possíveis. O predicado deve chamar-se \textit{valid\_moves(+Board, +Player, -ListOfMoves)}.

% TODO complete
\subsection{Play execution} 
Validação e execução de uma jogada num tabuleiro, obtendo o novo estado do jogo. O predicado deve chamar-se \textit{move(+Move, +Board, -NewBoard)}.

>>>>

@@

% TODO complete
\subsection{Board viewing} 
Before each move, the board is displayed on the screen. To display the board we use the predicate \textit{display\_game(+Board, +Player1, +Player2)}. This predicate first displays the players' names and then uses \textit{display\_board(+Board)} to display the board itself. 
The board is displayed line by line with a series of dividers. Although for game logic the values of the board can be positive or negative, the board is printed with only positive numbers.

% TODO complete
\subsection{List valid plays} 
As per requested, we developed a predicate that returns a list of all possible moves. This predicate is \textit{valid\_moves(+Board, -R)}. The first argument of the predicate is a list with the board of lines and board of blocks.
This predicate works by first finding a list of all empty cells with \textit{check\_all(+Board, -List),}. Then it tests all possible values in those cells with \textit{test_all(+List, +Board, +Result)}.

% TODO complete
\subsection{Play execution} 
Each player can make a move per turn \textit{player\_turn(+Board, +Player, -NewBoard)}. In this turn predicate, the program asks the player what he wants to play with \textit{get_move(-X, -Y, -V)} then the program tries that move with \textit{move(+Move, +Board, -NewBoard)}.
If the move is invalid the program repeats the previous action, otherwise, it returns a new board with the new piece.
